Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-27 arxiv-version/main.tex
Add proposition about Chebyshev polynomials

The idea behind all the mappings is that, on a compact set, multivariate
polynomials uniformly approximate any continuous function. This is result is a
special case of the well known Stone-Weierstrass theorem~\citep[Section
10.10]{Davidson-Donsig-2010}. In our case, we use a multivariate polynomial to
approximate the indicator function corresponding to the intersection of $K-1$
halfspaces. This polynomial separates examples in one class from examples in the
other classes. To be able to quantify $\gamma'$ and $R'$ as well as time
complexity of evaluating $k(x,x')$ we need to quantify certain parameters
of the approximating polynomial (degree, norm, range of values).
The parameters are quantified in \autoref{theorem:polynomial-approximation}
stated below.

@@

\begin{theorem}
\label{theorem:polynomial-approximation}
Let $w_1, w_2, \dots, w_K \in \R^d$ be such that $\sum_{i=1}^K \norm{w_1}^2 \le 1$.
Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
\begin{itemize}
\item $p(x) \ge 1$ for all $x \in \bigcap_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \ge \ip{w_i}{x} + \gamma \}$
\item $p(x) \le -1$ for all $x \in \bigcup_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \le \ip{w_i}{x} - \gamma \}$
\item $\deg(p) \le ???$
\item $\norm{p} \le ???$
\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
\end{itemize}
\end{theorem}

\subsection{Polynomials}
TODO

>>>>

The idea behind all the mappings is that, on a compact set, multivariate
polynomials uniformly approximate any continuous function. This is result is a
special case of the well known Stone-Weierstrass theorem~\citep[Section
10.10]{Davidson-Donsig-2010}. In our case, we use a multivariate polynomials to
approximate the indicator function corresponding to the intersection of $K-1$
halfspaces. This polynomial separates examples in one class from examples in the
other classes. To be able to quantify $\gamma'$ and $R'$ as well as time
complexity of evaluating $k(x,x')$ we need to quantify certain parameters
of the approximating polynomial (degree, norm, range of values).
The parameters are quantified in \autoref{theorem:polynomial-approximation-1}
and \autoref{theorem:polynomial-approximation-2}
stated below.

@@

\begin{theorem}[Polynomial approximation of intersection of halfspaces (1)]
\label{theorem:polynomial-approximation-1}
Let $w_1, w_2, \dots, w_K \in \R^d$ be such that $\sum_{i=1}^K \norm{w_1}^2 \le 1$.
Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
\begin{itemize}
\item $p(x) \ge 1$ for all $x \in \bigcap_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \ge \ip{w_i}{x} + \gamma \}$
\item $p(x) \le -1$ for all $x \in \bigcup_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \le \ip{w_i}{x} - \gamma \}$
\item $\deg(p) \le ???$
\item $\norm{p} \le ???$
\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
\end{itemize}
\end{theorem}

\begin{theorem}[Polynomial approximation of intersection of halfspaces (2)]
\label{theorem:polynomial-approximation-2}
Let $w_1, w_2, \dots, w_K \in \R^d$ be such that $\sum_{i=1}^K \norm{w_1}^2 \le 1$.
Let $\gamma > 0$. There exists a polynomial $p:\R^d \to \R$ such that
\begin{itemize}
\item $p(x) \ge 1$ for all $x \in \bigcap_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \ge \ip{w_i}{x} + \gamma \}$
\item $p(x) \le -1$ for all $x \in \bigcup_{i=2}^K \{ x \in \R^d ~:~ \ip{w_1}{x} \le \ip{w_i}{x} - \gamma \}$
\item $\deg(p) \le ???$
\item $\norm{p} \le ???$
\item $|p(x)| \le ???$ for all $x \in \R^d$ such that $\norm{x} \le 1$
\end{itemize}
\end{theorem}

The proofs of the theorems can be found in
Sections~\ref{section:proof-of-polynomial-approximation-1}~and~\ref{section:proof-of-polynomial-approximation-2}
respectively.

\subsection{Proof of \autoref{theorem:polynomial-approximation-1}}
\label{section:proof-of-polynomial-approximation-1}
TODO

\subsection{Proof of \autoref{theorem:polynomial-approximation-2}}
\label{section:proof-of-polynomial-approximation-2}

To construct the polynomial $p$ we use Chebyshev polynomials of the first kind.
Chebyshev polynomials of the fist kind form an infinite sequence of polynomials
$T_0(z), T_1(z), T_2(z), \dots$ of single real variable $z$. They are defined
by recurrence
\begin{align*}
T_0(z) & = 1 \; , \\
T_1(z) & = z \; , \\
T_{n+1}(z) & = 2zT_n(z) - T_{n-1}(z) & \text{for $n \ge 1$.}
\end{align*}

\begin{proposition}
Chebyshev polynomials satisfy for any $n \ge 0$
\begin{enumerate}
\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$.
\item If $z > 1$ then $T_n(z) \ge 1 + n^2(z - 1)$.
\item Absolute value of all coefficients of $T_n(z)$ is at most $2^n$.
\end{enumerate}
\end{proposition}
